\documentclass[draft=false
              ,paper=a4
              ,twoside=false
              ,fontsize=11pt
              ,headsepline
              ,BCOR10mm
              ,DIV11
              ]{scrbook}
\usepackage[ngerman,english]{babel}
%% see http://www.tex.ac.uk/cgi-bin/texfaq2html?label=uselmfonts
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%\usepackage[latin1]{inputenc}
\usepackage{libertine}
\usepackage{pifont}
\usepackage{microtype}
\usepackage{textcomp}
\usepackage[german,refpage]{nomencl}
\usepackage{setspace}
\usepackage[xindy]{imakeidx}
\usepackage{listings}
%%\usepackage{natbib}
\usepackage[ngerman,hidelinks]{hyperref}
\usepackage{soul}
\usepackage[printer]{hawstyle}
\usepackage{lipsum} %% for sample text
\usepackage{etoolbox}
%% All my packages
\usepackage{chngcntr}
\counterwithout{footnote}{chapter}
\usepackage{dirtree}
\definecolor{grey}{HTML}{E6E6E6}
\usepackage{realboxes}
\usepackage{amsmath}
\usepackage{framed}
\usepackage[amsmath,standard,hyperref,framed]{ntheorem}
\usepackage{tabu}
\usepackage{multirow}
\usepackage{pgf-umlsd}
\usepackage{bytefield}
\usepackage{float}
\usepackage{csquotes}
\usepackage[sorting=none,backend=biber,citestyle=numeric,doi=true,url=true]{biblatex}
\addbibresource{sample.bib}
%%\usepackage{amsthm}
\usepackage{parskip}

\usepackage{siunitx}
\sisetup{detect-all = true, free-standing-units = true}
%%\usepackage{xindy}
\usepackage[nomain,toc,acronym,xindy]{glossaries}

%%\usepackage{tocloft}
\usepackage{tocbibind}
\graphicspath{{./res/}{./logo/}}

\input{glos.tex}
\input{customs.tex}
%%\newacronym{dap}{DAP}{Debug access port}
%%\newacronym{tap}{TAP}{test access port}
\makeglossaries
%%\renewcommand{\cftdot}{.}
%%\renewcommand*{\familydefault}{\sfdefault}
\makeatletter
%%\patchcmd{\chapter}{\if@openright\cleardoublepage\else\clearpage\fi}{\par}{}{}
\renewcommand\fs@ruled{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
%%\def\@fs@post{\hrule height.8pt depth0pt \kern2pt}%
\def\@fs@post{\relax}
\def\@fs@pre{\kern2pt\hrule\kern8pt}%
\def\@fs@mid{\kern8pt\hrule\kern2pt}%
\let\@fs@iftopcapt\iffalse}
\makeatother
\usepackage{minitoc}
%% define some colors
\colorlet{BackgroundColor}{gray!20}
\colorlet{KeywordColor}{blue}
\colorlet{CommentColor}{black!60}
%% for tables
\colorlet{HeadColor}{gray!60}
\colorlet{Color1}{blue!10}
\colorlet{Color2}{white}

%% configure colors
\HAWifprinter{
  \colorlet{BackgroundColor}{gray!20}
  \colorlet{KeywordColor}{black}
  \colorlet{CommentColor}{gray}
  % for tables
  \colorlet{HeadColor}{gray!60}
  \colorlet{Color1}{gray!40}
  \colorlet{Color2}{white}
}{}
\lstset{%
  numbers=left,
  numberstyle=\tiny,
  stepnumber=1,
  numbersep=5pt,
  basicstyle=\ttfamily\small,
  keywordstyle=\color{KeywordColor}\bfseries,
  identifierstyle=\color{black},
  commentstyle=\color{CommentColor},
  backgroundcolor=\color{BackgroundColor},
  captionpos=b,
  fontadjust=true
}
\lstset{escapeinside={(*@}{@*)}, % used to enter latex code inside listings
        morekeywords={uint32_t, int32_t}
}
\ifpdfoutput{
  \hypersetup{bookmarksopen=false,bookmarksnumbered,linktocpage}
}{}

%% more fancy C++
\DeclareRobustCommand{\cxx}{C\raisebox{0.25ex}{{\scriptsize +\kern-0.25ex +}}}

\clubpenalty=10000
\widowpenalty=10000
\displaywidowpenalty=10000

% unknown hyphenations
\hyphenation{
}

%% recalculate text area
\typearea[current]{last}

\makeindex
\makenomenclature

\begin{document}
\selectlanguage{ngerman}
\floatstyle{ruled}
\restylefloat{figure}
%%%%%
%% customize (see readme.pdf for supported values)
\HAWThesisProperties{Author={Arne Wischer	}
                    ,Title={Design und Implementierung eines verteilten
                    linuxbasierten Entwicklungssystems für
                    Nahbereichsfunkanwendungen mit ARM-Architektur }
                    ,EnglishTitle={Design and implementation of a 
                    distributed Linux-based development platform for near-field
                    radio systems using the ARM architecture}
                    ,ThesisType={Bachelorarbeit} ,ExaminationType={Bachelorprüfung} ,DegreeProgramme={Bachelor of Science Technische Informatik} ,ThesisExperts={Prof. Dr. rer. nat. Hans Heinrich Heitmann
                    \and Prof. Dr.-Ing. Franz Korf} ,ReleaseDate={17. April
                    2013} }

%% title
\frontmatter
%%\input{planung}
%% output title page
\maketitle

\begin{spacing}{1}
%% add abstract pages
%% note: this is one command on multiple lines
\HAWAbstractPage
%% German abstract
{Entwicklungssystem, IEEE 802.15.4, OpenWRT, OpenOCD, Carambola, JTAG, GDB,
MIPS, ARM, UART}%
{Dieses Arbeit beschreibt die Entwicklung eines verteilten Systems, mit
dessen Hilfe eingebettete Funksysteme entworfen, implementiert und analysiert
werden können. Das System soll es einem Entwickler dabei ermöglichen,
viele dieser Entwicklungsschritte netzwerkgestützt durchzuführen. Da
beispielsweise auch die Funkdaten analysiert werden sollen, ist eine hohe
Genauigkeit der Datenerfassung notwendig. Realisiert wurde das
Entwicklungssystem mithilfe mehrerer MIPS-Entwicklungsboards, die als
"`Datenbrücken"' fungieren und JTAG-Steuerbefehle über GDB zur Verfügung
stellen sowie über UART gesammelte Daten an eine Clientanwendung durchreichen.
Diese Anwendung sortiert die eingehenden Daten nach ihrem Auftreten und zeigt
sie dem Entwickler an.\vspace{30pt}}
%% English abstract
{development platform, IEEE 802.15.4, OpenWRT, OpenOCD, Carambola, JTAG, GDB,
MIPS, ARM, UART}%
{This thesis describes the development of a distributed system to help
design, implement and analyze embedded radio systems. The system
allows a developer to perform many of these development steps with network
support. Since for example, the radio data needs to be analyzed, a high
accuracy while collecting data is necessary. The development system was
implemented using multiple MIPS development boards, working as "data
bridges" to provide JTAG-commands using GDB as well as provide data
collected via UART to a client application. This application sorts the incoming
data according to their occurrence and shows them to the developer.}
\end{spacing}
\mtcselectlanguage{german}
\dominitoc
\newpage

\begin{spacing}{0.97}
\tableofcontents
\end{spacing}
\singlespacing

\newpage
%% enable if these lists should be shown on their own page
%%\listoftables
%%\listoffigures
%\lstlistoflistings
\printglossary[type=acronym,title=Abkürzungsverzeichnis,toctitle=Abkürzungsverzeichnis]
%%\printglossaries
\adjustmtc
%% main
\mainmatter
\onehalfspacing
%% write to the log/stdout

\typeout{===== File: chapter 1}
%% include chapter file (chapter1.tex)o
\include{chapter1}
\include{chapter2}
\include{chapter3}
\include{chapter4}
\include{chapter5}

%%%%
%% add some text to generate a sample document
%\chapter{Sample Chapter}

%\lipsum

%%%%

%% appendix if used
\appendix
%%\typeout{===== File: appendix}
\include{appendix}

% bibliography and other stuff
%\backmatter

\typeout{===== Section: figures}
\listoffigures

\typeout{===== Section: literature}
%% read the documentation for customizing the style
%%\bibliographystyle{dinat}
%%\bibliography{sample}
\printbibliography[heading=bibintoc]

\typeout{===== Section: nomenclature}
%% uncomment if a TOC entry is needed
%%\addcontentsline{toc}{chapter}{Glossar}
\renewcommand{\nomname}{Glossar}
\clearpage
\markboth{\nomname}{\nomname} %% see nomencl doc, page 9, section 4.1
\printnomenclature

%% index
\typeout{===== Section: index}
\printindex

\HAWasurency

\end{document}
